Broom: Safe Region-Based Memory Management for Dataflow Programs

### 2015-11-04 paper/type-inference.tex
Edits.

Given a set of constraints, we first build a dependency graph ($G_c$)
with validity constraints as nodes, and dependencies between them
captured as edges. In particular, there exists an edge from a
constraint $c_2$ to a constraint $c_1$ in the graph if any of the
following conditions hold:
\begin{itemize}
\item $c_2$ and $c_1$ have atleast one common predicate variable
($\varphi$) that occurs positively in $c_2$ and negatively in $c_1$.
\item The set of predicate variables that occur negatively in $c_2$ is
a (non-strict) subset of the corresponding set for $c_1$.
\end{itemize}
The first condition intuitively corresponds to a case, where
expression or type, whose region elaboration is constrained by $c_2$
refers to a method or a class, whose unknown precondition is
constrained by $c_1$. The common predicate variable ($\varphi$)
represents the unknown precondition in this case. The dependency from
$c_2$ to $c_1$ means that $c_2$ must be solved to compute $\varphi$
before $c_1$ is solved, thus enforcing the rule that the precondition
of a method must not depend on its calling context. Since mutually
recursive definitions refer each other, the first condition also
results in bidirectional dependencies between mutually recursive
constraints (and self-loops over recursive constraints). The second
condition captures two kinds of dependencies. First, the dependency
from the constraints over a method precondition to the constraints
over the precondition of the class containing the method. This
captures our preference that the constraints over a class's region
parameters should not depend on the idiosyncracies of its methods. Any
additional constraints required by any of its methods must be captured
in the precondition of the method itself (well-formedness rules allow
this possibility). The second condition also adds bidirectional
dependencies between two validity constraints over same set of
predicate variables, thus requiring them to be solved simultaneously.

In the second step, we convert the dependency graph over constraints
into a dependency DAG ($G_C$) over sets of constraints, where each set
represents a strongly connected component in the dependency graph.
Constraints in each set are mutually dependent, and need to be solved
simultaneously, whereas constraints in different sets can be solved as
per any valid topological ordering of the graph. Accordingly, we
obtain a topological ordering of nodes in the graph $G_{{C}}$, and
solve the sets of constraints in that order. The solutions obtained
after solving a constraint set are applied to the constraints in
subsequent sets before attempting to solve them.

@@

We now formally define the constraint satisfaction problem over sets
of constraints. For simplicity, we ignore mutual recursion and assume
that a a set only contains (possibly recursive) constraints over a
single predicate variable. The general form of such a set of
constraints is as following:
\begin{center}
\(
  \bigcup_{i=1}^n \{
    \isvalid{\phictxt^{i} \conj \varphi}
            {\phicstr^{i} \conj \bigwedge_{k=1}^n F_k(\varphi)}
  \}
\)
\end{center}
The solution to the above set of constraints is a tuple $(\substFn,)$
problem is to find a map $$

>>>>

Given a set of constraints, we first build a dependency graph ($G_c$)
with validity constraints as nodes, and dependencies between them
captured as edges. In particular, there exists an edge from a
constraint $c_2$ to a constraint $c_1$ in the graph if any of the
following conditions hold:
\begin{itemize}
\item $c_2$ and $c_1$ have atleast one common predicate variable
($\varphi$) that occurs positively in $c_2$ and negatively in $c_1$.
\item The set of predicate variables that occur negatively in $c_2$ is
a (non-strict) subset of the corresponding set for $c_1$.
\end{itemize}
The first condition intuitively corresponds to a case, where
expression or type, whose region elaboration is constrained by $c_2$
refers to a method or a class, whose unknown precondition is
constrained by $c_1$. The common predicate variable ($\varphi$)
represents the unknown precondition in this case. The dependency from
$c_2$ to $c_1$ means that $c_1$ must be solved to compute $\varphi$
before $c_2$ is solved, thus enforcing the rule that the precondition
of a method must not depend on its calling context. Since mutually
recursive definitions refer each other, the first condition also
results in bidirectional dependencies between mutually recursive
constraints (and self-loops over recursive constraints). The second
condition captures two kinds of dependencies. First, the dependency
from the constraints over a method precondition to the constraints
over the precondition of the class containing the method. This
captures our preference that the constraints over a class's region
parameters should not depend on the idiosyncracies of its methods. Any
additional constraints required by any of its methods must be captured
in the precondition of the method itself (well-formedness rules allow
this possibility). The second condition also adds bidirectional
dependencies between two validity constraints over same set of
predicate variables, thus requiring them to be solved simultaneously.

Next, we convert the dependency graph over constraints into a
dependency DAG ($G_C$) over sets of constraints, where each set
represents a strongly connected component in the dependency graph.
Constraints in each set are mutually dependent, and need to be solved
simultaneously, whereas constraints in different sets can be solved as
per any valid topological ordering of the graph. Accordingly, we
obtain a topological ordering of nodes in the graph $G_{{C}}$, and
solve the sets of constraints in that order. The solutions obtained
after solving a constraint set are applied to the constraints in
subsequent sets before attempting to solve them.

@@

We now formally define the constraint satisfaction problem over sets
of constraints. For simplicity, we ignore mutual recursion and assume
that a a set only contains (possibly recursive) constraints over a
single predicate variable. The general form of such a set of
constraints is as following:
\begin{center}
\(
  \bigcup_{i=1}^n \{
    \isvalid{\phictxt^{i} \conj \varphi}
            {\phicstr^{i} \conj \bigwedge_{k=1}^n F_k(\varphi)}
  \}
\)
\end{center}
% The solution to the above set of constraints is a tuple $(\substFn,)$
% problem is to find a map
